Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Add comment for @kazu
Fix grammar issues

Haskell~\cite{haskell} has a very strong type system, which ensures that most type errors are
detected at compile time rather than runtime.  Thanks to this, we assume that
programs written in Haskell have less bugs than programs written in programming
languages that do not provide such a strong type system.

Unfortunately, the type system of Haskell does not always guarantee
correct semantics.
For example, it does not ensure that division by zero does not occur.
Another example is laws of type classes.
For instance, the {\tt Monoid} class has three Monoid laws
that its instance \emph{should} satisfy
but
it is the programmers responsibility to ensure that
instance definitions \emph{behave} as \emph{expected}.

@@

\noindent Note that the {\tt placeholders} library provides better keywords such as {\tt notImplemented} and {\tt todo}, which tells source locations when executed.
Next we write user documentation in Haddock markup:

>>>>

Haskell~\cite{haskell} has a strong type system, which ensures that most type errors are
detected at compile time rather than runtime.  Thanks to this, we assume that
programs written in Haskell have less bugs than programs written in programming
languages that do not provide such a strong type system.

Unfortunately, the type system of Haskell does not always guarantee
correct semantics.
For example, it does not ensure that division by zero does not occur.
An other example is, that instances of {\tt Monoid} \emph{should} be
monoids in the mathematical sense, but the type system does not
enforce this.  It is the programmers responsibility to ensure that
instance definitions \emph{behave} as \emph{expected}.

@@

\noindent Note that the {\tt placeholders} library provides better
keywords such as {\tt notImplemented} and {\tt todo}, which tells
source locations when executed.
\begin{quote}
    sol: @kazu Would it be fine with you to remove the reference to
    placeholders?

    \begin{itemize}
        \item Do we need it to make our point?
        \item It requires template-haskell and additional import, and
            is thus not very practical.
    \end{itemize}
\end{quote}

Next we write user documentation in Haddock markup:
